Non-word repetition in Yélî Dnye

### 2021-11-10 manuscript.Rmd
trying to generate track changes version

Additionally, we only had a single person interacting with children as well as interpreting children's production, so we do not know to what extent our findings generalize to other experimenters and research assistants. Furthermore, since both stimuli presentation and production data collected were audio-only, neither the children nor our research assistant were able to integrate visual cues in their interpretation. Although we know from other work that adults' perceptual performance on these types of sounds is well above chance from audio-only presentation [REF],  language processing for the majority of children will be audiovisual in natural conditions, and thus it may be interesting in the future to capture this aspect of speech.

>>>>

Additionally, we only had a single person interacting with children as well as interpreting children's production, so we do not know to what extent our findings generalize to other experimenters and research assistants. Furthermore, since both stimuli presentation and production data collected were audio-only, neither the children nor our research assistant were able to integrate visual production cues in their interpretation.  Other work shows that children's performance reaches ceiling by 12 years of age for auditorily-presented minimal pairs for typologically rare (i.e., pre- vs post-alveolar stop) contrasts [@casillasIPmarkedness]. Nonetheless,  language processing for the majority of children will be audiovisual in natural conditions, and thus it may be interesting in the future to capture this aspect of speech.
